### 2024-01-23 iterative_monomorphisation.tex
table

\begin{center}
\captionof{table}{Monomorphisation to the service of Zipperposition?}
\begin{tabular}{lccc}
   \toprule
   &portfolio classic & portfolio monomorphisation & custom portfolio \\
   \midrule
   bounds  & -  & - & - \\
   bounds2 & - & - & - \\
   bounds3 & - & - & - \\
   bounds4 & - & - & - \\
   bounds5 & - & - & - \\

   \bottomrule
\end{tabular}
\end{center}

\bigskip
\bigskip
\bigskip

\begin{center}
\captionof{table}{Monomorphisation as an alternative to native polymorphism?}
\begin{tabular}{lccccccccc}
   \toprule
   & \multicolumn{2}{c}{E}   & \multicolumn{2}{c}{Vampire} &\multicolumn{2}{c}{Leo3} & \multicolumn{2}{c}{Satallax} \\
   \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
   & native & mono & native & mono & native & mono & native & mono\\
   \midrule
   bounds  & - & - & - & - & - & - & - & - \\
   bounds' & - & - & - & - & - & - & - & - \\
   bounds* & - & - & - & - & - & - & - & - \\
   bounds? & - & - & - & - & - & - & - & - \\
   \bottomrule
\end{tabular}
\end{center}

>>>>

\subsection{Parameter optimisation}

\subsection{Monomorphisation as preprocessor}

\begin{table}[h]
\caption{Evaluation of native polymorphism vs.\ monomorphisation}
\centering\begin{tabular}{@{}lccc@{}}
   \toprule
   & Native & Mono & Union \\
   \midrule
   E  &   & 0 & 0 \\
   Leo-III & 0 & 0 & 0 \\
   Satallax &  & 0 & 0 \\
   Vampire & 0 & 0 & 0 \\
   Zipperposition & 0 & 0 & 0 \\[1.5\jot]
   Total & 0 & 0 & 0 \\
   \bottomrule
\end{tabular}
\end{table}

\subsection{E as Zipperposition backend}

\begin{table}[h]
\caption{Evaluation of Zipperposition without E vs. with E}
\centering\begin{tabular}{@{}lccc@{}}
   \toprule
   & without E & with E & Union \\
   \midrule
   Zipperposition & 0 & 0 & 0 \\
   \bottomrule
\end{tabular}
\end{table}
